### 2023-10-17 README.Rmd
formatting

This repo contains code to generate simple and transparent prediction intervals for the IMF World Economic Outlook forecasts [1]. Central prediction intervals are generated at the 50% and 80% levels for CPI inflation and real GDP growth, based on past forecast errors. See below for documentation on which files the respective folders contain.

[1]: International Monetary Fund. 2023. \textit{World Economic Outlook: A Rocky Recovery.} Washington, DC. April.

@@

>>>>

This repo contains code to generate simple and transparent prediction intervals for the IMF World Economic Outlook forecasts (see references). Central prediction intervals are generated at the 50% and 80% levels for CPI inflation and real GDP growth, based on past forecast errors. See below for documentation on which files the respective folders contain.

@@

## References

International Monetary Fund. 2023. *World Economic Outlook: A Rocky Recovery.* Washington, DC. April.
